Phylogenetics and the human microbiome.

### 2013-09-28 sbreview.tex
Thank Olivier.

\section{Acknowledgements}
The author would like to thank Aaron Darling, David Fredricks, Noah Hoffman, Connor McCoy, Martin Morgan, and Sujatha Srinivasan for interesting discussions that informed this review.
FAM is supported in part by NIH R01 HG005966-01 and NSF Award 1223057.

>>>>

\section{Acknowledgements}
The author would like to thank Olivier Gascuel for the opportunity to present on this subject during the 2013 LIRMM Mathematical and Computational Evolutionary Biology workshop and for organizing a corresponding special section of \textit{Systematic Biology}.
He is also grateful to Aaron Darling, David Fredricks, Noah Hoffman, Connor McCoy, Martin Morgan, and Sujatha Srinivasan for interesting discussions that informed this review, and to support from the NIH (R01 HG005966-01) and NSF (1223057).
